% Template for articles for CCR (Computational Communication Research)
% Version 0.02

% This file contains information such as author, title, etc.
% Edit the body.tex file to add the contents (or change the \input{body} below)

\documentclass{ccr}

% Note - lines starting with a % are completely ignored by latex and function as comments
% See https://www.overleaf.com/read/hmwdsgcqkxrd for a complete example article

% The first part of the latex document contains metadata

% Regular metadata (title, authors etc)
\title{Automated Detection of Voice in News Text – Evaluating Tools for Reported Speech and Speaker Recognition}
\shorttitle{Automated Detection of Voice in News Text}
\authorsnames{Ahrabhi Kathirgamalingam, Fabienne Lind, Hajo G. Boomgaarden}
% Short author list for footer
\shortauthors{Kathirgamalingam et al.}

% Note that you need to provide as many affiliations as authors
% If multiple authors have the same affiliation, please copy that record as needed
\authorsaffiliations{
  {Computational Communication Science Lab, University of Vienna},
  {Computational Communication Science Lab, University of Vienna},
  {Computational Communication Science Lab, University of Vienna},
}

\abstract{
The automated content analysis of text has become integral to contemporary communication and journalism research. However, automated approaches are seldom utilized to analyze reported voice in text, while doing so would offer valuable insights into media and communication practices. Bridging the fields of communication science and computational linguistics, this study reviews and evaluates off-the-shelf tools for automated voice detection (of direct/indirect speech and of speakers) with respect to user experience and validity. Manually annotated English news articles and Twitter data served as baseline for evaluating the automated detection of voice. Findings indicate that the tools being assessed offer a satisfactory user experience and provide promising solutions for detecting direct speech automatically, encouraging fellow researchers to utilize automated detection for direct quotations. However, the recognition of indirect speech and speakers needs considerable improvement.
}
\keywords{automated voice detection, reported speech annotation, quote annotation, speaker annotation, quote attribution, automated content analysis}

% You can add or rename the bibliography file(s) here
% Note that you can exported them from endnote or zotero directly and upload them to overleaf
\addbibresource{bibliography.bib}


% The following information is provided by the journal when moving to production
\volume{5}
\pubnumber{1}
\pubyear{2023}
\firstpage{85}
\doi{10.5117/CCR2023.1.004.KATH}

% some packages that are generally useful when writing articles in latex
\usepackage{tabularx}  % for full-width tables
\usepackage{booktabs}  % for nicer horizontal lines in tables
\usepackage[mode=text]{siunitx} % for centering columns on the decimal mark
\usepackage{graphicx} % for including figures
\usepackage[hidelinks]{hyperref} % for URLs and other hyperlinks

\begin{document}
\maketitle

% Include the body
% Note: You can also type it directly here, or include a file per section, whatever works best for you

% The article body
% Also see main.tex for information such as authors, title, abstract, etc
% See https://www.overleaf.com/learn/ for some great resources on learning latex

%Regular text is written as plain text.
%You can write an entire paragraph in one line,
%or split lines in any way you want

%You can use an empty line to start a new paragraph.

\section{Automated Detection of Voice in News Text}The digitization of both research objects and tools has greatly affected research in communication science and journalism studies and the development of computational methods to meet the emerging possibilities and challenges is increasing (\cite{bennett1990toward, hepp2016kommunikations, löblich2010empirisch}). While generally automated approaches to content analysis are nowadays quite commonly applied (\cite{van2018communication}), the specific method of automated voice analysis is seldom addressed in communication and journalism research. By ‘voice’ we refer to the direct or indirect speech of actors as reported in text. Thus, voice detection includes the identification and extraction of any reported speech as well as the attribution of speech acts to certain actors or actor categories. Since the practice of incorporating actors (i.e., people, organizations) or other sources such as documents in text and the embedding of the quoted statements is prevalent and highly relevant in journalism and media communication (\cite{berkowitz2009reports}), automated voice analysis presents a potentially very important approach for communication and journalism scholars. Detecting actors’ voices in text, for example, allows to shed light on journalists’ work with sources (e.g., Reich, 2011) or to compare arguments or opinions of various mentioned actors. The empirical examination of reported speech in news content (e.g.,\cite{bennett1990toward}) has largely been based on manual content approaches (e.g.,\cite{crawley2016victims, fengler2020stumme}). Yet, there are also efforts to automate the detection of voice in text (\cite{krestel2008minding, lazaridou2017identifying, pouliquen2007automatic}). A considerable part of these tools can be attributed to developers from computational linguistics (e.g., \cite{brunner2015automatische, elson2010automatic, he-etal-2013-identification, muzny2017two, o2012sequence}), with some important contributions also coming from communication scholars (e.g., \cite{krestel2008minding, pouliquen2007automatic, scheible2016model, welbers2021extracting}). Beyond the developers' reports, there is little to no literature on the performance of these automated voice detection tools and the tools are rarely used by other researchers than the developers themselves. Keeping this in mind and considering that methods critically shape the research questions we raise and the problems we solve (\cite{waldherr2019messinstrumente}), this study focuses on reviewing potential approaches to automate the detection of reported speech from persons and organizations in textual data. By evaluating off-the-shelf tools, we intend to raise their visibility and ultimately seek to contribute to their wider application.

More specifically, we reviewed and tested three natural language processing tools that offer the immediate recognition of voice in English: CoreNLP (\cite{manning2014stanford}), QSample (\cite{scheible2016model}), and rsyntax (\cite{welbers2021extracting}). We evaluated the selected tools in respect to user experience and focused here on aspects such as required user skills, output data structure, and post-processing. The validity of the tools is assessed through a comparison of the tools’ coding decisions to manual coding decisions. Our manually coded benchmark consists of 200 English news articles and 400 English tweets, yielding 1.851 instances of reported speech with corresponding speakers. This way, we test the tools jointly on a variety of text types. We explain which tool is more suitable for which sub task (direct speech, indirect speech, and speaker detection) and provide recommendations for their usage in automated content analysis tasks.

In what follows, we first discuss the theoretical need for voice detection, before moving on to a reflection on the automation of the detection of voice in text. Subsequently, we review available voice detection tools and discuss their quality assessment.

\section{Examining Voices}Since methodological choices impact the validation of existing theories and the construction of new theories (\cite{hepp2016kommunikations, mahrt2015mit, strippel2018zukunft}), the usability and particularly the validity of new methodological approaches cannot be examined isolated from theory. Several theoretical approaches reflecting on voice in media provide grounds for empirical investigations. To name a few, theories query on journalistic rationales of including voices, e.g., to cross-check (\cite{reich2011source}), to increase credibility (\cite{gans1979deciding}), to construct a certain objectivity (\cite{tuch1972}), or on the aspects determining who is included and who is not such as newsworthiness (\cite{reich2011source}), proximity to media production and elitism (\cite{hall1978policing}), or socio-demographics such as gender and ethnicity (\cite{bennett1990toward, benson2009makes, hall1978policing}). Other theories consider the promises and pitfalls of being included as a speaker (e.g., \cite{berkowitz2009reports, manning2001news}).
To empirically address these theories conducting an analysis of voices is useful. Voice analysis focuses on detecting and analyzing direct and indirect speech from persons, organizations, or other sources such as documents incorporated in textual data. Thereby, the analysis allows insights into presence, absence and distributions of speakers, and on the content level of the reported speech itself.

Considering existing voice analyses by means of manual analysis (e.g., \cite{crawley2016victims, fengler2020stumme, thorbjornsrud2016marginalized}) a few observations are noteworthy. First, scholars detect both direct and/ or indirect quotations. Second, only a few studies explain the coding rules in more detail (e.g., \cite{carpenter2008source, thorbjornsrud2016marginalized}). Third, for both kinds of speech, verbs of speaking - so-called \textit{verba dicendi} (e.g., say) play a significant role. Fourth, in case of direct speech, quotation marks are crucial (\cite{thorbjornsrud2016marginalized}). Fifth, the person or organization that is the source of the voice is coded and some studies coded other characteristics of a speaker such as socio-demographics(e.g., \cite{crawley2016victims}). Sixth, many studies combined voice analysis with other content analyses, such as framing (e.g., \cite{brown2017changing, thorbjornsrud2016marginalized}).

The current state of manual investigation techniques in communication science presents challenges such as high costs, imprecision, and poor inter-coder reliability. These challenges, along with the richness of theoretical frameworks that deal with voices, justify the need to explore the potential capacities of automated voice analysis.

\section{Automating Voice Detection}Efforts to apply new digital opportunities to voice detection have been initiated since the 2000s (e.g., \cite{pouliquen2007automatic}). The main body of literature can be situated in computational linguistics, where voice analysis enables, for example, the investigation of literary texts (\cite{brunner2015automatische, elson2010automatic, muzny2017two}). Advancing interdisciplinary research, computational linguistics approaches are also considered for communication and journalism science purposes.
The techniques underlying text-as-data approaches can be grouped in three umbrella categories. Some approaches to automating voice detection rely on rule-based techniques where punctuation, morphological, and syntactic patterns (e.g., \cite{krestel2008minding}) or dictionaries with the names of speakers and \textit{verba dicendi} (e.g., \cite{pouliquen2007automatic}) are used. Others rely on supervised machine learning models where annotation rules are learned from pre-coded samples (e.g., \cite{scheible2016model}).Yet, unsupervised machine learning approaches offer also great potential as seen in related fields (\cite{boumans2016taking}).

Voice detection, strictly speaking, consists of several different tasks,and these tasks can be assigned to two main categories: reported speech and voice attribution (\cite{muzny2017two}). Defining the first category, reported speech detection refers to the annotation of speech. Researchers distinguish between direct and indirect speech (e.g., \cite{pouliquen2007automatic, scheible2016model}). Some additionally consider mixed speech (e.g., \cite{pareti2013automatically}). Direct speech is fully enclosed in quotation marks and is a verbatim reproduction of the original utterance. Indirect quotations paraphrase the original utterance without quotation marks. Mixed quotations contain both verbatim and paraphrased content (\cite{pareti2013automatically}).\textit{Verba dicendi} are central for all reported speech forms (\cite{pareti2013automatically, lazaridou2017identifying}). Further, and complicating voice analysis, there are many variations to both direct and indirect speech (e.g., implicit or explicit quotes). There are also many instances of phrases that are not reported speech but follow similar rules (e.g., use of quotation marks for titles) and \textit{verba dicendi} that are used in other contexts (\cite{scheible2016model}).

Moving on to the second category, voice attribution is the detection of the source of the reported speech (\cite{muzny2017two}). Some researchers distinguish between extracting speaker entities and extracting mentions (\cite{muzny2017two}). While a speaker entity is the concrete source of the quote, the mention is the attribution that is given closest to the quote (e.g., pronoun or reference) and later helps to identify the speaker entity. Here, too, there are different approaches to detecting the attribution. While computational linguists can often work with a predefined list of the possible actors in their text (e.g., \cite{he-etal-2013-identification}), this is rather challenging for communication and journalism scholars dealing with news. Another possibility is to incorporate databases with possible actors such as Wiki Data, but these might miss actors that are less or not prominent.

\subsection{Tools for Voice Detection}Serving the two main tasks described above, a number of tools have
evolved over the past two decades. We now review tools that were identified via a comprehensive online search, performed in 2021. As part of this search, we scanned open source platforms such as \textit{GitHub} as well as studies and reports by the tool developers. All reviewed tools process English language data, but differ with respect to the specific voice detection task(s) they perform and regarding their methodological approach to voice detection.

\textcite{pouliquen2007automatic} were among the early developer teams to contribute a voice detection solution for the communication science research community. They describe a rule-based tool that retrieves direct speech and speakers from a large set of news reports. The tool was developed for eleven languages within the framework of NewsExplorer. The logic behind their approach is to look for quotation markers in combination with \textit{verba dicendi} and person names from a list of possible names (\cite{pouliquen2007automatic}). Accordingly, only quotes that meet these three conditions would be found.

The Reported Speech Tagger (RST) by \textcite{krestel2008minding} is built for the GATE framework. GATE (General Architecture for Text Engineering) is a continuously complemented Open-Source toolkit providing text analysis and language processing solutions. RST detects direct and indirect speech and returns the attributed speaker with a set of six patterns with varying position of verba dicendi, speaker and reporting clause (\cite{krestel2008minding}).

In the realm of supervised machine learning, \textcite{elson2010automatic} propose to treat speaker detection as a classification task. The approach first identifies potential speakers in a text and assigns to each reported speech the most likely speaker, unlike relying on the closest speaker to a quote span. This method was designed for literary texts and therefore uses a gold standard from this domain.

Based on the work of \textcite{o2012sequence} who consider quote attribution as a sequence labeling task and who experiment with different classifiers and configurations, \textcite{pareti2013automatically} introduce a model that is later extended in \textcite{pareti2015attribution}. This pipeline detects cues (\textit{verba dicendi}) with the help of a token-level k-NN classifier and then uses the cue in combination with linear-chain conditional random field (CRF) to locate the quote. This pipeline detects direct and indirect quotations.

\textcite{scheible2016model} identified that the correct identification of the beginning and end of a quote is challenging for some existing tools and suggests improvements proceeding from the CRF setting from \textcite{pareti2013automatically}. \textcite{scheible2016model} propose a semi-Markov sequence model that smooths the Markov assumption and therefore incorporates global features into the classification task. Other than only the presence of \textit{verba dicendi}, \textcite{scheible2016model} find the frequency of \textit{verba dicendi} in each reported speech of importance. The semi-Markov model outperforms \textcite{pareti2015attribution}. The resulting supervised machine learning based tool, called QSample, is able to detect direct and indirect speech for English data.

Stanford CoreNLP, a well-known pipeline framework for various NLP tasks such as tokenization, part-of-speech tagging and named entity recognition, also offers a tool for direct speech and speaker detection called Quote Extraction and Annotation (\cite{manning2014stanford}).The annotator was provided by \textcite{muzny2017two} who combined the rule-based approach to direct speech annotation from \textcite{o2012sequence} with a two-stage sieve approach to detect not only the attributed mentions but also the speaker entities. The two stages of the algorithm consists of first linking the quote to the mention and then linking the mention to the speaker. For both steps different deterministic techniques such as rule-based patterns, dependency parsing, co-referencing, and others are used (\cite{muzny2017two}). Due to missing records, it is rather challenging to state which techniques from \textcite{o2012sequence} and \textcite{muzny2017two} are included in the currently available CoreNLP pipeline.

Another approach to voice detection is an R package that allows querying syntactic dependency trees called rsyntax. This package was first presented as part of a case study (\cite{vanatteveldt2017clause}) and later updated with more information on its solutions for voice detection (\cite{welbers2021extracting}). Rsyntax provides functions for querying direct and indirect speech and also speakers from tokenized data. The querying relies on information on the token’s relation to other tokens in a sentence due to a prerequisite step of dependency parsing. Since this package can be combined with different language models it can be potentially utilized for languages other than English.

\section{Quality Assessment of Tools}
Assessing the quality of automated voice detection tools, we concentrate on user experience and validity as primary criteria.

User experience focuses on the users’ interaction with a service and describes their overall impression (\cite{hassenzahl2006user}). Tools need to be user-oriented and feedback from external users is significant for their evaluation and further development. Different suggestions exist on which aspects should be examined to assess user experience (\cite{laugwitz2006konstruktion}). Here, user experience implies aspects that may be decisive for the use of automated tools for voice detection from communication and journalism scholars’ perspective: accessibility, required technical infrastructure, required skills and expertise, required data preparations, needed post-processing of the outcomes, and overall strengths and weaknesses of the tools. Up to this point, there are no reports on the user experience of the tools reviewed for this study.

The second and crucial criterion for quality assessment is validity. Validity is ensured when the tool measures what it is supposed to measure (\cite{krippendorff2004reliability}) and is described as a significant challenge for computational methods. Testing validity is necessary for developing a tool (\cite{grimmer2013text}) and measuring validity by comparing the computational output with a gold standard is a standard procedure. The developers of the tools mentioned above rely on and report parameters such as precision, recall, and F1 scores (\cite{pareti2013automatically, muzny2017two, scheible2016model}). A direct comparison of these reported parameters is quite misleading, as the nature of the evaluation for each tool differs, especially as they are validated based on different data sources. Thus, to jointly assess the validity of the presented voice detection tools we propose the implementation of an identical evaluation protocol for all tools.

A quality assessment by external researchers comparing several tools with each other is not yet available for voice detection tools. While voices are very relevant from a communication and journalism science perspective, and tools to automatically detect them are also continuously being developed, the application of these tools is often rather rare and mostly by the developers of the tools. The aim of this study is, thus, to provide guidance and a systematic comparison of different tools with the aim of leading to more frequent and better use of the tools.

\section{Data \& Methods}
\subsection{Data Selection}
Since the tool review presented here primarily addresses communication science and journalism researchers, we selected a variety of news texts and tweets for the tool performance test. In line with the limited language capabilities of the tools, we chose English language news texts. The selected data contain news texts from two different media types: newspapers and social media. Analyzing voice in newspapers is a major application field in communication science and journalism studies. Newspaper content follows systematic punctuation rules and provides a certain text quality, which increases the chances of high quality computational annotation. To review the tool's performance on newspaper data with variation in reporting style, we utilize 100 newspaper articles from traditional and tabloid papers from UK and USA: \textit{The Guardian}, \textit{Daily Mirror}, \textit{Washington Post}, and \textit{USA Today}. Additionally, we have a more specialized dataset of newspaper articles on migration from the research project 'Role of European Mobility and its Impacts in Narratives, Debates and EU Reforms' (REMINDER) (\cite{IEGQ1B_2020}). The focus on migration texts is motivated by previous manual analyses that examine the representation of migrants' voices in news coverage (e.g., Brown et al., 2017; Thorbjørnsrud \& Figenschou, 2016). The specialized dataset consists of 100 news articles from the tabloid outlet \textit{Daily
Mirror} and the traditional outlet \textit{The Guardian} both from the UK. The second selected media type is social media communication, which is another major field of observation, but rarely examined in terms of reported speech. Thus, by manually coding and automatically annotating, we may infer the value of voice detection for shorter text with potentially different reporting style and syntactic structures. We make use of a Twitter dataset that consists of 50 randomly sampled tweets from each of the mentioned outlets (\textit{Daily Mirror}, \textit{The
Guardian}, \textit{Washington Post}, \textit{USA Today}) and added 100
tweets from each, the Twitter account of UK right-wing alternative news
blog \textit{Guido Fawkes} (order-order.com) and more left-wing
alternative news blog \textit{AlterNet} (alternet.org). These randomly
sampled 400 tweets were posted between 2016 and 2018.

\subsection{Tool Selection}Among the previously discussed tools (see page 6), we have selected all
those that were off-the shelf and available. Thus, no longer available
tools were discarded from the selection (e.g., \cite{elson2010automatic, krestel2008minding, pareti2015attribution, pouliquen2007automatic}). Based on
this requirement, the quotation detection tool of the CoreNLP pipeline
(\cite{manning2014stanford}), QSample (\cite{scheible2016model}), and rsyntax
(\cite{welbers2021extracting}) were selected to evaluate user experience and
validity. All three tools are available via~\textit{GitHub}. The pipeline
CoreNLP includes a rule-based technology to detect direct speech and
speaker, QSample relies on supervised machine learning to detect direct and
indirect speech, and rsyntax queries dependency trees to extract both types of reported speech and the speakers.
\subsection{Methodology}We evaluate the automated voice detection tools with a three-step
process: First, we automatically annotate the text sample with the tools
and provide a comprehensive documentation of the user experiences.
Second, we annotate the same text sample manually to build a reference
corpus. Third, the automatically and manually detected information is
compared. In the following, each step is described in detail.

\textit{\textbf{Automated Annotation}}

In the first step, the sampled data were automatically annotated with
the selected tools, CoreNLP, QSample, and rsyntax. Meanwhile, to
evaluate the user experience, a systematic documentation of the
implementation was conducted by following a predefined set of categories (see Online Appendix A\footnote{\url{https://osf.io/sq5hj/}}). The categories cover the comprehensive process of automated annotation in terms of user experience: installation process, required technical infrastructure, required input data structure, required skills from user, other specific preparations, output data structure, and required post-processing.

\textit{\textbf{Manual Annotation}}

Three trained human coders annotated direct and indirect speech and the
speaker of the reported speech for each text of the presented sample
based on a set of coding rules (see Online Appendix B). The coding rules
resemble the rules of the tools evaluated here to ensure comparability.
Any verbatim quote containing quotation marks is coded as direct speech.
Mixed quotations that combine direct and indirect speech within one
sentence are coded as direct speech. If a sentence contains more than
one word or phrase in quotation marks, each word combination is coded as
a separate quote. Multi-paragraph quotations, however, are coded as one
comprehensive direct quote. Indirect quotations are coded by
identifying~\textit{verba dicendi}~combined with a reported clause and a
speaker. In practice, it appeared to be challenging to distinguish
between indirect quotations and interpretative statements by authors. In
these cases, the full text as well as context knowledge about the
presented story needed to be considered to decide. Additionally, we
extracted the speakers of the quotes. The speaker entity can be a
person, an organization, or another source that is quoted such as
documents. In many cases, however, the speaker of the quote is mentioned
by a pronoun or a reference (e.g., the president) in the close
surroundings of the quote. Here, the context was considered to identify
the correct speaker entity. We coded both, the speaker entity and the
mention. If there was no speaker indicated, we coded `Unknown' as the
tools should also be able to recognize that there is no speaker.

To ensure the quality of the manually coded reference corpus, an
inter-coder reliability test was conducted with all three coders for 10
randomly selected articles and 20 randomly selected tweets. The coders
were able to extract up to 47 cases of reported speech from the articles
and 8 cases of reported speech from the tweets. In terms of newspaper
annotating, we achieved a Krippendorff's alpha = .83 for the detection
of direct speech. The identification of indirect speech yielded a
Krippendorff's alpha = .74, confirming the mentioned difficulties in
detecting indirect speech. For the speaker annotation, the
Krippendorff's alpha was = .74. For the annotation of the Twitter
data, we yielded a Krippendorff's alpha = 1 for direct speech, alpha = .93
for indirect speech, and alpha = .93 for speaker detection.

The manual annotation resulted in three reference datasets\footnote{The annotations for the general news, specialized news and Twitter dataset are available here: \url{https://osf.io/f6pt9/}} providing information on article level (amount of direct and indirect
quotations) and quotation level (type of reported speech, the extracted
quote, and speaker). Table~\ref{tab:manual} summarizes the results of the manual
annotation.
% Note that in latex, tables and figures are 'floats' and will not be set directly where
% you type them, but in a location that matches the general style, usually at the top of a page
% You can include a position hint such as the 't' below, other options are 'b' (bottom) and 'h' (here)
\begin{table}[t]
    \centering
        \caption{Amount of manually coded quotes and speakers per dataset}
    % Label for cross-references, you can use any name here that you want
    \label{tab:manual}
    % Note: Xlcr in the line below specifies 3 columns with 'X', 'l', 'c', 'r', and 'S' as column types.
    % The first column (X) is for teXt, and will be expanded to fill the width of the table
    % The other three columns will be just wide enough to fit the contents,
    % and will be aligned left, center, and right respectively
    % The last column uses the 'S' type from the 'siunitx' package, which aligns on decimal marks
    % Note that if you want to have regular text in such columns (e.g. in the header),
    % you need to enclose it in {curly braces}
    \begin{tabularx}{\textwidth}{Xccccc}
    % Table rows use & to separate cells and end with \\
    % Use \toprule, \midrule and \bottomrule for the horizontal lines
    \toprule
    & Reported S. & Direct S. & Indirect S. & Speaker & {Mention}\\
    \midrule
    General newspaper & 958&558 & 400 & 756 & 202 \\
    Specialized newspaper & 810 & 577 & 233 & 578 & 232 \\
    General Twitter & 83 & 63 & 20 & 80 & 3 \\
    \midrule
   Total & 1851 & 1198 & 653 & 1414 & 437  \\
    \bottomrule
    \end{tabularx}
    \raggedright\footnotesize\sffamily{\textit{Note}. S = Speech, Reported Speech = Direct and Indirect Speech. General news dataset \textit{n} = 100 articles, Specialized news dataset \textit{n} = 100 articles, General Twitter dataset \textit{n} = 400 tweets.}

\end{table}

%As you can see, markup such as (sub)section headers are introduced using latex commands starting with a backslash.
%You can use \textit{italic} and \textbf{bold} text as needed.

In total, manually annotating all three datasets resulted in 1.851
reported speech consisting of 1.198 direct and 653 indirect speech. Further, 1.414 speaker entities and 437 speaker mentions were annotated.
Table 1 presents the distribution of the manually annotated
quotes between the datasets. The high amount of reported speech,
especially direct speech, indicates its importance in journalistic
reporting and encourages communication and journalism researchers to
empirically assess this field. In the sampled tweets, however, reported
speech occurs rather less frequently.

\subsection{Comparison of Automated and Manual Annotation} The automated annotation results were then systematically compared with the manual results to assess the validity of the voice detection tools.
A combination of automated and manual cross-checking enabled tracking
true positives, false positives, and false negatives. The three
categories were used to calculate precision, recall, and F1 scores
(\cite{goutte2005probabilistic}) for each tool by task and by dataset. For
the speaker annotation, we calculated two recall, precision, and F1
scores per task and dataset. Both versions were only calculated for the
reported speech that were correctly extracted by the tools. In the first
version, automatically detected speaker entities and mentions were both
considered correct. The second version only considers speaker entities
(and not mentions such as pronouns) as sufficient.

As another method to identify possible shortcomings of the tools, we conducted a classification error analysis by manually checking the false positives and false negatives.

\section{Results}
In the following, we present how CoreNLP, QSample, and rsyntax performed
with respect to user experience and in contrast to the manual coding
decisions.

\subsection{User Experience}CoreNLP's website delivers well-documented information on the installation of CoreNLP and the required files (\cite{manning2014stanford}). Ideally, the input data is organized in plain text files. Although CoreNLP detects most different quotation marks in addition to regular quotation marks, embedded quotations need to be marked by differing punctuation (\cite{manning2014stanford}). The documented command initiates other pipeline applications such as tokenizer and sentence splitter, that are required to successfully run the quote extraction and attribution.

As a result of fast processing, CoreNLP creates output files for each input file. The extracted quotes and speakers are enlisted with the assigned index per quote and information on the byte where the quote begins, presented as follows: \textit{Speaker: ``Quote'' {[}index = X, charOffsetBegin = Y{]}}.

Similar to CoreNLP, QSample can be downloaded from \textit{GitHub}
(\cite{scheible2016model}) and provides well-documented installation steps.
The implementation requires \textit{Java} (\textgreater= 1.7) and
\textit{Maven} (\textgreater= 3.0.0) to be preinstalled and to run the
command. QSample requires the input text files gathered in a specific
folder. QSample's command then processes the input data and creates
tokenized output files with words and punctuation as units. Each token
is assigned to a label: C, B, E, I, or 0. If the token is assigned a
zero, it is not part of a quote. Label 'C' identifies a token as a cue for
a quote, while 'B' marks the beginning, 'E' the ending, and 'I' the span
of the quotation. QSample does not categorize the detected quotes into
direct and indirect speech. For most purposes, researchers need to
reassemble the relevant tokens in a post-processing step. Even though only
minimal coding knowledge was required to run the tool, expertise in
coding and data management are required for post-processing.

Rsyntax is available either from the Comprehensive R Archive Network
(CRAN) or as a developer version on \textit{GitHub}. The input files are
first processed using NLP applications such as \textit{spaCy} or \textit{UDpipe}, which are applied for dependency parsing. For the queries applied to the resulting dependency parsed data, users need to set a list of \textit{verba dicendi} (see Online Appendix C for the list used here). This is an important step, as it decides which reported speech clauses are extracted by rsyntax. Based on the predefined list of \textit{verba dicendi} and the dependencies of the tokens, rsyntax searches for specific patterns that are indicated by queries. This process yields labels per token (e.g., quote and source) that can be used in a post-processing step to extract reported speech and speaker. Using rsyntax with the published codes does not provide any information on the type of reported speech. However, the queries can be easily customized and reformulated to suit various needs. As \textcite{welbers2021extracting} describe, some basic understanding of R and especially data frames is necessary to utilize the package.

\subsection{Comparison of Automated Annotations to Manual Baseline and Error
Analysis}

Regarding validity, Table~\ref{tab:validity} shows the number of automatically extracted
annotations and the validity scores by task and dataset per tool. The
results of the classification error analysis are addressed here to
provide more insight into the contexts of the validity scores.

CoreNLP was used to tag direct speech and the related speakers and
annotated -- for all three datasets together -- 1401 direct quotes and
corresponding speakers. Assessing CoreNLP's annotations for the general
newspaper dataset reveals sufficient precision values (.85) and very
high recall (.99), leading to a high F1 score (.91). Results were
similar for the specialized migration dataset (precision = .79, recall
.90, F1 score = .84). For the Twitter data, precision was considerably
lower (.60), while recall was still high (.90), which resulted in a
passable F1 score (.72). A closer examination of the false positives
revealed that most difficulties occurred for phrases written in
quotation marks without being a quote (e.g., titles). Inspecting the few
false negatives reveals that CoreNLP struggles with quotations when a
space is missing before or after the quotation mark.

For the task of speaker detection and with permitting mentions, CoreNLP
performed with passable precision (.72), recall (.72) and F1 score (.72)
for the general newspaper dataset, while the values were lower for the
specialized newspaper dataset with precision (.49), recall (.54) and F1
score (.52). The speaker annotation of the Twitter data, however,
yielded a precision of .60, a recall of .54 and, therefore, an F1 score
of .57. With restricting true positives to speaker entity
recognition and excluding mention detections, CoreNLP performed poorer for all three dataset.\footnote{
General newspaper dataset: Precision = .58, recall = .57, F1 score =
57; Specialized newspaper dataset: Precision = .37, recall = .40, F1 score = .38; General Twitter dataset:
Precision = .51, recall = .46, F1 score = .48} Examining the
misclassification points to a potential problem of other entities and
mentions in the close surroundings or within the reported speech.


%Quotations can be given latex style for `single' or ``double'' quotations marks,
%or a bit easier using the "csquotes" packages included above.
%You can also copy-paste the ‘smart quotes’ directly from e.g. MS Word.

% Note that in latex, tables and figures are 'floats' and will not be set directly where
% you type them, but in a location that matches the general style, usually at the top of a page
% You can include a position hint such as the 't' below, other options are 'b' (bottom) and 'h' (here)
\begin{table}[t]
    \centering
        \caption{Comparison of Automated Annotations to Manual Baseline}
    % Label for cross-references, you can use any name here that you want
    %   \begin{tablenotes}
    %  \small Note. Precision, Recall and F1 score are calculated based on the manually annotated results % reported in Table 1. Reported validity scores for speaker detection are calculated based on speaker % entities and mentions.
  %  \end{tablenotes}
    \label{tab:validity}

    % Note: Xlcr in the line below specifies 3 columns with 'X', 'l', 'c', 'r', and 'S' as column types.
    % The first column (X) is for teXt, and will be expanded to fill the width of the table
    % The other three columns will be just wide enough to fit the contents,
    % and will be aligned left, center, and right respectively
    % The last column uses the 'S' type from the 'siunitx' package, which aligns on decimal marks
    % Note that if you want to have regular text in such columns (e.g. in the header),
    % you need to enclose it in {curly braces}
    \begin{tabularx}{\textwidth}{Xccccccccc}
    % Table rows use & to separate cells and end with \\
    % Use \toprule, \midrule and \bottomrule for the horizontal lines
    \toprule
     & \multicolumn{2}{c}{Reported Speech} & \multicolumn{3}{c}{Direct Speech} & \multicolumn{2}{c}{Indirect Speech} & \multicolumn{2}{c}{Speaker}\\
     \cmidrule{2-3} \cmidrule(l){4-6} \cmidrule(l){7-8}  \cmidrule(l){9-10}
    Tool & {\tiny QSample} & {\tiny rsyntax} & {\tiny CoreNLP} & {\tiny QSample} & {\tiny rsyntax}  & {\tiny CoreNLP} & {\tiny QSample} & {\tiny CoreNLP} & {\tiny rsyntax}  \\
    \midrule
    \multicolumn{10}{l}{General newspaper dataset - 100 articles}\\
    \IE \textit{N} & 1172 & 827 & 651 & 492 & 370 & 680 & 457 & 551 & 661 \\
    \IE P & .75 & .80 & .85 & .90 & .94 & .64 & .68 & .72 & .93 \\
    \IE R & .82 & .68 & .99 & .85 & .62 & .77 & .72 & .72 & .76\\
    \IE F1 & .79 & .74 & .91 & .88 & .75 & .70 & .70 & .72 & .83 \\
     \addlinespace
  \multicolumn{10}{l}{Specialized newspaper dataset - 100 articles}\\
    \IE \textit{N} & 1011 & 747 & 655 & 464 & 380 & 547 & 367 & 634 & 552 \\
    \IE P & .69 & .74 & .79 & .96 & .94 & .46 & .53 & .49 & .88 \\
    \IE R & .80 & .66 & .90 & .77 & .64 & .81 & .72 & .54 & .60\\
    \IE F1 & .74 & .70 & .84 & .85 & .76 & .59 & .60 & .52 & .72 \\
     \addlinespace
   \multicolumn{10}{l}{General Twitter dataset - 400 tweets}\\
    \IE \textit{N} & 38 & 57 & 95 & 21 & 25 & 17 & 32 & 59 & 35 \\
    \IE P & .66 & .61 & .60 & .71 & .95 & .59 & .44 & .60 & .89 \\
    \IE R & .28 & .42 & .90 & .24 & .32 & .50 & .70 & .54 & .37\\
    \IE F1 & .39 & .50 & .72 & .36 & .48 & .54 & .54 & .57 & .53 \\
    \bottomrule
    \end{tabularx}
    \raggedright\footnotesize\sffamily{\textit{Note}. \textit{N} = Amount of detected speech or speaker, P = Precision, R = Recall, F1 = F1 score. Precision, Recall, and F1 score are calculated based on the manually annotated results reported in Table 1. Reported validity scores for speaker detection are calculated based on speaker entities and mentions.
}
\end{table}

QSample annotated 2.221 instances of reported speech (direct and
indirect). Describing the results for the detection of reported speech
in general newspaper dataset, we observed a precision of .75 and a high
recall of .82, leading to a F1 score of .79. For the specialized
newspaper dataset we achieved similar results (precision = .69, recall =
.80, F1 score = .74), for Twitter, the scores were much lower. Here, the tool
performed with a precision of .66, a recall of .28 and F1 score of .39.
We further used quotation marks as indicators for direct speech, to see
if we can find any differences in the tool's performance for direct and
indirect speech annotation. In both newspaper datasets, the F1 scores
were considerably higher for direct speech tagging (.88 and .85) than
for indirect speech annotation (.70 and .59). In the case of Twitter
data, however, the direct speech tagging performed poorer (F1 score= .36)
than the indirect speech tagging (F1 score = .54) because precision (.71) and
recall (.24) were much more imbalanced for direct speech than for
indirect speech. The few false positives for the direct speech detection
point to the same problems that were found with CoreNLP regarding
quotation marks. A reason for the false negatives was that QSample was
not able to detect multi-paragraph quotes. A closer look at the false
positives and false negatives for the indirect speech detection does not
provide much insight. QSample splits many annotated quotes into two or three parts for an
indistinct reason, which makes it difficult to find clear patterns. Possibly, this might be due to subordinate clauses
(e.g., The person, who\ldots) and, therefore, more complex sentence
structures.

Moving on to the third tool in review, rsyntax was tested with respect
to reported speech (direct and indirect) as well as speaker annotation.
Rsyntax performed with high precision for both general (.80) and
specialized news content (.74), while recall is lower (.68 and .66),
leading to an F1 score above .70 for both. For Twitter, the tool
annotated with a precision of .61 and a low recall of .42, resulting in
an F1 score of .50. Here too, we distinguished between direct and
indirect speech by considering quotation marks as indicators. This way,
it was possible to find that precision for direct speech was much higher
for all data types (above .94) than for indirect speech, while recall
was higher for indirect speech annotation than for direct speech (.72
for both newspaper data and .70 for Twitter), leading to similar F1
scores between direct and indirect annotation across all three datasets.
Taking a closer look at the false positives reveals that rsyntax
extracted phrases including \textit{verba dicendi} from the predefined
list with a different meaning (e.g., Our politicians once told the
truth). Also, subordinate clauses within sentences were misclassified as
reported speech sometimes (e.g., The person, who did not reveal his
surname). In terms of false negatives, rsyntax missed to annotate direct
speech quotes that are entirely written in quotation marks without any
dependencies to other tokens outside of the quotation marks. In a few
cases, false negatives resulted from \textit{verba dicendi} that were
missing from the predefined list.

Lastly, rsyntax showed a good performance for speaker detection with an
F1 score of .83 for general news and of .72 for specialized news, with
precision being higher than recall. For annotating speakers for the
tweets, the tool shows high precision (.89) and low recall (.3),
resulting in an F1 score of .53. With restricting the true positives to
correctly matched speaker entities, not mentions, the validity
decreases.\footnote{General newspaper dataset: Precision = .60, recall = . 56, F1 score =
.58; Specialized newspaper dataset: Precision = .83, recall = .49, F1 score = .62; General Twitter dataset:
Precision = .86, recall = .36, F1 score = .51} Examining the false
positives, we find that mostly tokens that introduce a subordinate
clause and therefore show a more complex dependency structure are
misclassified as speakers (e.g., who). Also, the singular and plural
first-person pronouns (I and we) are often incorrectly tagged as
speakers, especially in cases where a person reports themselves within a
reported speech (e.g., I say we\ldots).

\section{Discussion}

A research field that can benefit a lot from computational methods is
the investigation of reported speech in textual data. The existing
impulses in automated methods for voice detection have been rarely used
in applied research, although they promise relief for the labor-intense
challenge of data collection and annotation. This study addressed the
usability and validity of automated approaches for voice detection.

Overall, we can state that the user experience of the tools evaluated
here was highly satisfactory, while validity differed considerably
across tools, but also across tasks and data domains. This leads us to
recommend different tools for different tasks and data types. To detect
direct speech in newspaper and Twitter data, we recommend CoreNLP.
Further, we suggest utilizing rsyntax for reported speech (i.e., direct
and indirect speech) and speaker annotation in newspaper data. While
QSample is worth considering for the annotation of reported speech in
newspaper data, we find that flexibility and potential for improvements
speak in favor of rsyntax.

In the following, we discuss user experience and validity in greater
detail before heading to a detailed discussion on our overall evaluation
and recommendations.

\subsection{User-Experience}

The here reviewed tools, CoreNLP, QSample, and rsyntax, provide a
comparable user experience in most of the evaluated points. They provide
a rather easy-to-implement download and installation process. The
required technical infrastructures are well-documented. It may take some
effort to set up all prerequisites. Further, the tools provide straightforward commands that reduce the
requirements on coding skills considerably and provide results in only a
few minutes.

We observed more significant differences in the structure of the output
and the required post-processing for subsequent analyses. While CoreNLP assembles all extracted quotations in
a specific order, QSample and rsyntax return the articles in tokenized
manner with annotations. For post-processing, experience in coding and
data structures come in very handy. As an advantage, rsyntax outputs can
be post-processed without switching the environment, which can be an
asset if users have some experience with coding in R.

In summary, the tools offer solid user experience and are
more comprehensible and customizable for more experienced coders,
especially in regard to post-processing.

\subsection{Validity}

In comparison to the values that \textcite{muzny2017two} report for CoreNLP
(precision = .89, recall = .75, F1 score = .81), the F1 score of the presented
annotation for direct speech does not differ remarkably, while precision
and recall do. In our analysis, CoreNLP performs somewhat poorer yet
still satisfactory in terms of precision and better in respect to
recall. Taking some loss on recall into account, a possible solution for
a better precision value that can be derived from the error analysis
would be to exclude extracted direct speech with less than two words.

For the CoreNLP speaker detection, \textcite{muzny2017two} report a
precision of .9, a recall of .65, and an F1 score of .75. When accepting
mentions as correct annotations in addition to speaker entities, CoreNLP
performs similar to the report in the case of general news and even
better in case of Twitter data, while the scores are poorer for the specialized newspaper data on migration. By using the two-stage sieve approach to
track from quote to mention and from mention to speaker entity, CoreNLP
promises to track the speaker entity correctly even if only a reference
to it is present in the direct surrounding of a quote. Our results
indicate that this promise is not fully realized.

In the case of QSample, the reported indicators (precision = .79, recall
= .71, F1 score = .75) refer to the annotation of direct and indirect
speech (\cite{scheible2016model}). While the overall F1 score achieved in
our automated annotation is similar to the reported outcome, we obtained
a lower precision and a higher recall. As we distinguish between direct
and indirect speech, a deeper insight is needed here. The scores of the
direct speech are substantially better than those of the quotations
overall, except for the Twitter data, where the poor recall for direct
speech strongly lowers the F1 score. QSample flags only a few passages
as direct quotes that are none in the view of our manual coding while
also tracking down an acceptable proportion of manually identified
quotes in the data set.

For the newspaper data, the validity measures for indirect speech of
QSample are poorer than the overall outcome that \textcite{scheible2016model}
reported. For the Twitter data, however, the validity is better than for
direct speech, albeit still not passable. A rather broad definition of
indirect speech could lead to the disagreements with the manual
baseline. Yet, the results are in line with the literature indicating
that indirect speech is rather challenging to detect \textcite{pareti2013automatically}

\textcite{welbers2021extracting} do not report any specific validity values.
However, they anticipate that the usage of rsyntax for reported speech
provides a good precision, while the improvement of recall is dependent
on setting queries that can extract the different shapes of reported
speech. Using the queries provided on their \textit{GitHub} repository,
our results match these arguments, precision is higher than recall. The
balanced F1 score, however, indicates that the tool is acceptable for
newspaper data. For the Twitter data, rsyntax is just as unsuitable in
terms of validity as QSample. Similar to QSample, rsyntax performs
better for direct speech than for indirect speech. While both tools
perform similarly for indirect speech, QSample returns better F1 scores
for direct speech as recall is higher. The speaker detection of rsyntax
yields good F1 scores for the newspaper datasets, especially for the
general news data. Thus, the validity of speaker detection for Twitter
is considerably poorer.

Since it is possible to fine-tune the rsyntax queries, the validity
could be improved. We suggest extending the code so that it can extract
reported speech with the entire quote between quotation marks and other
more specific formulations of reported speech. Further, as our
classification error analysis shows, the \textit{verba dicendi} list
offers potential to improve validity by finding a balance between more
and less straightforward verbs. Optimizing the classification of the
reported speech might also enhance the validity for speaker detection.

\section{Overall Performance and Recommendations}The evaluation of both, user experience and validity, allows us to make
more specific recommendations based on each data type and task, and
moreover a few general ones.

In terms of data types, we evaluated CoreNLP, QSample, and rsyntax on
newspaper articles and on tweets from news media. The evaluation of all
three tools revealed that reported speech detection performs
considerably better with text that follows a more sophisticated writing
style and is lengthier such as newspaper. For shorter text data such as
tweets and other social media posts, we limit our recommendation to
direct speech detection with CoreNLP.

In terms of tasks, our results indicate that detecting direct speech
works much better than detecting indirect speech. The decision to
extract only direct speech is also justifiable as many manual voice
analysis studies also limit to direct speech and speaker. For the
detection of direct speech, we recommend using CoreNLP for both
newspaper data and tweets. The implementation requires only little
coding and data management knowledge, and all outputs can be further
processed easily. In terms of validity, CoreNLP provides high values for
direct speech annotations, while the speaker recognition performs only on a
sufficient level for general newspaper data with permitting mentions
(e.g., pronouns or references). In addition, other aspects highlight the
benefits of CoreNLP: The possibility to combine voice detection with
other NLP tasks and the potential to solve emerging issues by querying
community platforms such as Stack Overflow as CoreNLP is widely used.
The chance for a long-lasting availability and further development of
CoreNLP is high.\footnote{We further recommend monitoring the functionalities of stanza, which
is just as Core NLP, another open source general NLP library by the Stanford NLP group.
https://stanfordnlp.github.io/stanza/index.html While it includes no
specific operation for quote detection yet, the NLP package has
received a lot of attention by the community in recent year and is
likely to do so in the next years as well.}

For the detection of direct and indirect speech as well as of speakers
in newspaper data, rsyntax appears to be a good fit. Our recommendation
here is especially based on the flexibility of the tool that allows
optimizing the recall by adding further query rules and by fine-tuning
the list of \textit{verba dicendi}. Accordingly, the validity scores
reported here can be understood more as an initial point. \textcite{welbers2021extracting} also offer a \textit{GitHub} repository\footnote{rsyntax recipe repository: \url{https://github.com/kasperwelbers/rsyntaxRecipes}
 } that is updated regularly. Lastly, we assume R to be a
widely utilized coding language in communication sciences, which makes
the tool even more approachable.

If there is no research interest in the speakers, QSample might be worth
considering. While the post-processing is somewhat more difficult
compared to the other tools, QSample is well usable, too. In terms of
validity, it performs slightly better than rsyntax overall. However, the
possibility to improve these values is not as easy as with rsyntax,
which is designed more transparently.

By directly comparing three off-the-shelf tools considering user
experience and validity issues, it can be said that the tools are not
yet flawless and need further development. Nevertheless, the reviewed
tools offer solutions that prove to be very suitable, at least
partially. The performance for direct speech recognition is very
satisfactory and highly recommended for research in this area, as the
tools score in user experience and validity. For indirect speech and
speaker detection, however, there is potential to improve. Nevertheless,
the utilization of automated approaches for the detection of direct
speech itself is already a major addition to scientific practice, and
the outcomes of the here presented review may encourage fellow
researchers to make use of the possibilities in this regard.~Considering
the effort and costs of human annotation, a software tool that is easily
scalable can relieve researchers of some work.

\section{Conclusion}

First and foremost, we recommend considering automated approaches to
voice detection in general. The amount of manually annotated quotes in
our sample (see Table 1) indicates the relevance of detecting and
analyzing voices. While our recommendations mainly refer to the use of
direct speech detection in longer news articles, we strongly advise to
always conduct a pretest with a small sample to detect easily solvable
problems, e.g., regarding punctuation systems, or revalidating before applying the
tools on larger datasets.

The presented findings here must be seen in the light of some
limitations. Validating tools with a manually created baseline which is
in itself not free from error is rightfully subject to criticism but
still one of the most appropriate benchmarks available (\cite{song2020validations}). Further, the complexity in evaluating user experience is to
assess whether errors of the automated tools hinge on the user's
expertise or point out the error-proneness of the tools.~Lastly, by
concentrating on off-the shelf tools in our comparison, we naturally
only dealt with other voice detection tools in passing.

The ongoing innovative and interdisciplinary drive in computational
social science, however, allows assuming that approaches to voice
detection will continue to evolve. Regarding future research, our
recommendations tackle three fields: First, as the detection of indirect
speech and speakers holds potential, further research should optimize
existing techniques or investigate new approaches for voice detection.
Secondly, research needs to evaluate the proposed software more and also
from an external perspective. Methods, as emphasized, impact not only
what we observe but also how and what conclusions we draw from our
observation. Therefore, it is crucial to evaluate methods and draw new
impulses for improvement. Especially transformer model based approaches
are worth exploring next. Similarly, the promising and up-to-date
applications for other languages such as STWR for German (\cite{brunner2020bert}) or multilingual solutions (e.g., \cite{byszuk2020detecting}) also
give much reason for closer examination.

This leads to our final and most significant recommendation: to apply
existing tools in research on voices. Although the
applications do not provide flawless results, they are useful, as
presented here. It is evident that reported speech is an
extensively applied technique already and continues to be a relevant
field of interest for communication and journalism studies.


\section{Supplementary Materials}
All supplementary materials can be found at:
\url{https://osf.io/2g3a8/}


\section{Acknowledgements}
We would like to thank Arun Raveendran and Hannah Kronschnabl for their valuable assistance and insightful comments throughout this project. Further, we would also like to thank the Horizon 2020 project REMINDER (Grant agreement ID: 727072) for providing resources and support for this research project.
% Bibliography

% Uncomment the next line (\nocite{*}) if you want to include all items from your .bib file
% (e.g. if you didn't use the \textcite or \parencite commands above)
\nocite{*}

% This command generates the bibliography
\printbibliography
\end{document}
