% Template for articles for CCR (Computational Communication Research)
% Version 0.02

% This file contains information such as author, title, etc.
% Edit the body.tex file to add the contents (or change the \input{body} below)

\documentclass{ccr}

% Note - lines starting with a % are completely ignored by latex and function as comments
% See https://www.overleaf.com/read/hmwdsgcqkxrd for a complete example article

% The first part of the latex document contains metadata

% Regular metadata (title, authors etc)
\title{Candidate Party, Gender, and the Face Mask as a Political Symbol in Campaign Advertisements}
\shorttitle{Party, Gender and Face Masks}
\authorsnames{Jielu Yao, Travis N. Ridout, Markus Neumann, Erika Franklin Fowler}
% Short author list for footer
\shortauthors{Author \& Second}

% Note that you need to provide as many affiliations as authors
% If multiple authors have the same affiliation, please copy that record as needed
\authorsaffiliations{
  {East Asian Institute, National University of Singapore, Singapore},
  {School of Politics, Philosophy and Public Affairs, Washington State University, Pullman, USA},
  {Duke Kunshan University, China},
  {Department of Government, Wesleyan University, Middletown, USA}
}

\abstract{During the COVID-19 pandemic, wearing a face mask became politicized in the United States, with politicians and reporters employing competing public safety and civil liberties frames in discussions of masking. In this research, we argue that political candidates’ decisions to speak about and depict mask-wearing in their political advertising were strategic, depending on both the candidate's party and gender. We examine political ads run on Facebook and on television by federal candidates during the 2020 U.S. campaigns. We use Amazon’s deep learning algorithms for PPE (personal protective equipment) detection. We extract the text and audio of each ad to identify mentions of masks and use an à la Carte embedding regression model to understand how the usage of the term mask differs across covariates. We find that images of masks are much more common than mentions of masks, that there are significant partisan, but not gender, differences in the use of masks, and that there are both partisan and gender differences in the way that candidates speak about masking.  This research demonstrates the utility of a novel approach to collecting data. It also suggests that public health measures can become partisan in a campaign environment, with the potential to polarize both the views and behaviors of Democrats and Republicans.}
\keywords{masks, COVID-19, political advertising}

% You can add or rename the bibliography file(s) here
% Note that you can exported them from endnote or zotero directly and upload them to overleaf
\addbibresource{bibliography.bib}


% The following information is provided by the journal when moving to production
\volume{7}
\pubnumber{1}
\pubyear{2025}
\firstpage{1}
\doi{10.5117/CCR2025.1.2.YAO}

% some packages that are generally useful when writing articles in latex
\usepackage{tabularx}  % for full-width tables
\usepackage{booktabs}  % for nicer horizontal lines in tables
\usepackage[mode=text]{siunitx} % for centering columns on the decimal mark
\usepackage{graphicx} % for including figures
\usepackage{csquotes}\MakeOuterQuote{"}  % to allow "double quotes" instead of ``double quote''
\usepackage[hidelinks]{hyperref} % for URLs and other hyperlinks
\usepackage{biblatex}
\usepackage{amsmath}
\usepackage{subfig}

\newcommand{\sym}[1]{\textsuperscript{#1}}

\begin{document}
\maketitle

\input{body}


% Bibliography

% Uncomment the next line (\nocite{*}) if you want to include all items from your .bib file
% (e.g. if you didn't use the \textcite or \parencite commands above)
% \nocite{*}

% This command generates the bibliography
\printbibliography
\newpage

\appendix
\input{appendices}

\end{document}

